Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Conclusion.tex
CAV doesn't appear to be single blind.  Add authors

We illustrated a direct realization of our proposed proof framework for a
concrete MSI cache coherence protocol implementation codifying the intuition
behind the system's correctness as simple invariants. While this took
significant effort, once done, we showed that many key hardware
modifications,\eg{} replacement policies, could be made with a very small
addition to the proof. These bits were small enough that an informed hardware
designer implementing our protocols can reasonably be expected to provide such
additional proofs during refinement, producing a provably correct realistic
cache coherence engine implementation.

The protocol framework we showed was very flexible, and could easily be
extended for variants that go beyond micro-architectural variants, \eg{}
extension to MOSI with a relatively small amount of additional reasoning. This
gives us good confidence that we can effectively produce frameworks for other
classes of protocols, \eg{} update-based protocols, non-inclusive cache
hierarchies. Further, nothing about our methodology requires we limit ourselves
to cache coherence systems; this approach should naturally extend to any
hardware-based system.

While fundamentally this work meets our goal of verification of synthesizable
hardware specifications, there is still some important mechanization to make
this ready for industrial use. Foremost, the simple transliteration between the
inductively defined transition system in Coq and the Bluespec hardware
description should be fully mechanized.
%Further, the proposed extension to provide fairness of transaction scheduling
%in the Bluespec compiler should be implemented.
Further, to fully guarantee correctness of the resulting hardware, we should
also verify the hardware synthesis compiler, possibly using FeSi~\cite{Tomas}.

>>>>

%% We illustrated a direct realization of our proposed proof framework for a
%% concrete MSI cache coherence protocol implementation codifying the intuition
%% behind the system's correctness as simple invariants. While this took
%% significant effort, once done, we showed that many key hardware
%% modifications,\eg{} replacement policies, could be made with a very small
%% addition to the proof. These bits were small enough that an informed hardware
%% designer implementing our protocols can reasonably be expected to provide such
%% additional proofs during refinement, producing a provably correct realistic
%% cache coherence engine implementation.

%% The protocol framework we showed was very flexible, and could easily be
%% extended for variants that go beyond micro-architectural variants, \eg{}
%% extension to MOSI with a relatively small amount of additional reasoning. This
%% gives us good confidence that we can effectively produce frameworks for other
%% classes of protocols, \eg{} update-based protocols, non-inclusive cache
%% hierarchies. Further, nothing about our methodology requires we limit ourselves
%% to cache coherence systems; this approach should naturally extend to any
%% hardware-based system.

%% While fundamentally this work meets our goal of verification of synthesizable
%% hardware specifications, there is still some important mechanization to make
%% this ready for industrial use. Foremost, the simple transliteration between the
%% inductively defined transition system in Coq and the Bluespec hardware
%% description should be fully mechanized.
%% %Further, the proposed extension to provide fairness of transaction scheduling
%% %in the Bluespec compiler should be implemented.
%% Further, to fully guarantee correctness of the resulting hardware, we should
%% also verify the hardware synthesis compiler, possibly using FeSi~\cite{Tomas}.

### 2014-02-06 paper/Title.tex
CAV doesn't appear to be single blind.  Add authors

\author{
%    Muralidaran Vijayaraghavan\\Massachusetts Institute of Technology\\vmurali@csail.mit.edu\and
%    Nirav Dave\\SRI International\\ndave@csl.sri.com\and
%    Adam Chlipala\\Massachusetts Institute of Technology\\adamc@csail.mit.edu\and
%    Arvind\\Massachusetts Institute of Technology\\arvind@csail.mit.edu
}

>>>>

%% \author{
%% %  \adamc{Fill in authors, including Richard or any other appropriate additions}
%%    Muralidaran Vijayaraghavan\\Massachusetts Institute of Technology\\vmurali@csail.mit.edu \and
%%    Nirav Dave\\SRI International\\ndave@csl.sri.com \and
%%    Adam Chlipala\\Massachusetts Institute of Technology\\adamc@csail.mit.edu \and
%%    Arvind\\Massachusetts Institute of Technology\\arvind@csail.mit.edu
%% }

\author{Muralidaran Vijayaraghavan\inst{1} \and Nirav Dave\inst{2} \and Adam Chlipala\inst{1} \and Arvind\inst{1}}

\institute{{Massachusetts Institute of Technology,}\\{Computer Science and
    Artificial Intelligence Laboratory, Cambridge, MA, USA}\\\email{\{vmurali, adamc, arvind\}@csail.mit.edu} \and
           {SRI International, Computer Science Laboratory, Menlo Park, CA,
       USA}\\\email{ndave@csl.sri.com}}
